\documentclass[11pt]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0em}{}
\setlist{nosep, left=0pt}
\begin{document}

% =====================
% Header
% =====================
\begin{center}
    {\LARGE \textbf{Harsh Raj}}\\[3pt]
    \small
    Jamshedpur, Jharkhand, India $\vert$ +91-92634-01358 $\vert$ \href{mailto:myselfharshr@gmail.com}{myselfharshr@gmail.com} \\
    \href{https://github.com/primetree2}{github.com/primetree2} $\vert$ \href{http://www.linkedin.com/in/harsh-raj-820117173}{linkedin.com/in/harsh-raj-820117173}
\end{center}

\section*{Professional Summary}

Final-year Computer Science student with experience developing AI-powered applications, developer tools, and full-stack web platforms. Skilled in Python, JavaScript/TypeScript, React, FastAPI, PostgreSQL, and cloud deployment, with research experience in automated code refactoring and software quality evaluation.


\vspace{-2mm}
% =====================
% Education
% =====================
\section*{Education}

\noindent\textbf{VIT-AP University, Amaravati} \hfill \textit{Expected: September 2026}\\
B.Tech in Computer Science and Engineering, SCOPE \\
\textbf{CGPA: 8.56 / 10}

\vspace{0.8em}

\noindent\textbf{Vidya Bharati Chinmaya Vidyalaya, Jamshedpur} \hfill \textit{March 2022}\\
Senior Secondary School \\
\textbf{Class 10: 94.4\% \quad Class 12: 83.2\%}



% =====================
% Skills (ATS keywords)
% =====================
\section*{Skills}
\textbf{Languages:} Python, Java, JavaScript, TypeScript, SQL, HTML/CSS.\\
\textbf{Frameworks \& Libraries:} React, Next.js, FastAPI, Flask, TailwindCSS.\\
\textbf{Databases:} PostgreSQL, Supabase, Drizzle ORM.\\
\textbf{Tools \& Platforms:} Git, GitHub, AWS, Vercel, Railway, Google Cloud, N8N.\\
\textbf{AI/ML:} Machine Learning, NLP, Google API, OpenAI API, Prompt Engineering.\\

% =====================
% Selected Projects (bullet + impact + tech keywords)
% =====================
\section*{Projects}
\begin{itemize}

    \item \textbf{Argos - Competitive Live Debate Platform}
    \hfill \href{https://argos-indol.vercel.app}{\texttt{[Live Link]}} \\
    \textit{Tech: Next.js, TypeScript, Supabase, PostgreSQL, Drizzle ORM, Gemini AI, TailwindCSS, Vercel} \\
    Built a full-stack debate platform supporting 2--5 round competitive matches with AI evaluation across 4 scoring dimensions and detection of 10 logical fallacies. Engineered 15+ API routes, 8 database tables, real-time multiplayer synchronization, Google OAuth authentication, and Elo-based ranked matchmaking. Integrated Gemini AI for automated scoring and feedback generation, while deploying a scalable cloud architecture with public debate feeds, challenge lobbies, daily AI-generated topics, and automated debate lifecycle management.

    \item \textbf{MergeIQ - AI-Powered Pull Request Analyzer}
    \hfill \href{https://github.com/primetree2/mergeiq}{\texttt{[GitHub]}} $\vert$ \href{https://web-production-6f4dd.up.railway.app}{\texttt{[Live Link]}} \\
    \textit{Tech: Python, FastAPI, Chrome Extension (MV3), Gemini 2.5 Flash, GitHub REST API, PyJWT, Railway} \\
    Built a Chrome extension and GitHub App that automatically analyzes every pull request using Gemini AI, delivering structured verdicts (Safe / Review Needed / Risky) with risk flags, summaries, and suggested review questions. Fetches live repo context (README, folder structure, dependencies, recent commits) for project-aware analysis. GitHub App mode posts analysis comments autonomously on PR open via webhook, requiring zero manual interaction from contributors.

    \item \textbf{HealthAssist - AI Symptom Checker and Health Companion} 
    \hfill \href{https://health-assist-rose.vercel.app/}{\texttt{[Live Link]}} \\
    \textit{Tech: Python, FastAPI, React, TailwindCSS, Google API, Generative AI, Render, PostgreSQL} \\
    Implemented a web-application that generates detailed analyses of the symptoms provided by the patient including blood-report context-awareness, with personalized advices and precautions. Integrated 4 key data-points with 5 levels of analyses/advices.

    \item \textbf{CodeSage - AI code-base refactoring system and questions generator} 
    \hfill \href{https://codesage-724681386895.us-central1.run.app/}{\texttt{[Live Link]}} \\
    \textit{Tech: Python, Flask, React, TailwindCSS, Google API, Google Cloud, OpenAI API, LLMs} \\
    Implemented an AI code-base analysis and refactoring system that helps improve code quality, maintainability, and generates insights about your projects using Google's Gemini AI or other LLMs. Supports more than 15 programming languages. Conducted a detailed research report on the performance of 5 leading LLMs with different prompts and scoring metrics. Currently developing a cAST-based pipeline for cutting-edge refactoring capabilities. 

\end{itemize}

\section*{Research}

\textbf{Performance Evaluation of LLMs and Prompt Strategies for Automated Python Code Refactoring:} \\
Evaluated 4 frontier LLMs and 2 prompt-engineering strategies for automated Python code refactoring across 5 benchmark programs. Measured code quality and documentation improvements using BLEU, ROUGE-L, and Pylint metrics, achieving style-conformance scores of 9.2--9.7/10. Conducted comparative analysis of model and prompt performance to identify effective refactoring strategies.

% =====================
% Certifications & Achievements
% =====================
\section*{Certifications}

\begin{itemize}[leftmargin=*]
    \item \textbf{Data Analysis in R (DataCamp)} \hfill \href{https://github.com/primetree2/cisco-certificate/blob/main/certificate%20(1)_merged.pdf}{\texttt{[Link]}}
    \item \textbf{MERN Full Stack (Ethnus)} \hfill \href{https://github.com/primetree2/cisco-certificate/blob/main/3G3GLRGN.pdf}{\texttt{[Link]}}
    \item \textbf{AWS Certified Cloud Practitioner (AWS)} \hfill \href{https://github.com/primetree2/cisco-certificate/blob/main/AWS%20Certified%20Cloud%20Practitioner%20certificate.pdf}{\texttt{[Link]}}
    \item \textbf{Oracle OCI Generative AI Professional (Oracle)} \hfill \href{https://github.com/primetree2/cisco-certificate/blob/main/eCertificate.pdf}{\texttt{[Link]}}
    \item \textbf{Oracle Certified Foundations Associate (Oracle)} \hfill \href{https://github.com/primetree2/cisco-certificate/blob/main/oracle.pdf}{\texttt{[Link]}}
    \item \textbf{JavaScript Essentials (Cisco)} \hfill \href{https://github.com/primetree2/cisco-certificate/blob/main/22BCE7591_AP2023246000888_DA02.pdf}{\texttt{[Link]}}
    \item \textbf{Networking Essentials (Cisco)} \hfill \href{https://github.com/primetree2/cisco-certificate/blob/main/cisco%20networking%20essectials.pdf}{\texttt{[Link]}}
\end{itemize}



\section*{Achievements}
\begin{itemize}
    \item\textbf{2nd Place, The Return Journey Hackathon} (GDSC, IIT-Kanpur)
\end{itemize}

% =====================
% Experience / Roles (campus + leadership)
% =====================
\section*{Leadership \& Roles}
\begin{itemize}
    \item \textbf{Manager}, TEAM NEXT NEXUS (Prompt Engineering Club) \hfill July 2024 -- December 2024\\
    Led prompt-engineering study groups and reviewed generative-AI mini-project submissions, facilitating collaborative learning and technical discussions among club members.
    \item \textbf{Associate Manager}, Madhya Bharat Association (Cultural Club) \hfill July 2024--December 2024\\
    Oversaw event logistics and team coordination for cultural events with 50+ participants.
\end{itemize}

% =====================
% Additional
% =====================
\section*{Additional Information}
\textbf{Languages:} English (Proficient), Hindi (Native) \\
\textbf{Interests:} AI Research, Number Theory, Art/Animation, Content Creation

\end{document}